sensitivity_tests_march2025_tables_specialization

### 2025-07-31 Code/sensitivity_tests_march2025_tables_specialization.Rmd
Clean out repository for manuscript publication getting rid of old versions of data and code

---
title: "sensitivity_tests_march2025_tables"
author: "Kristin Dobbin"
date: "2025-04-14"
output: 
  html_document: default
  pdf_document: default
knit: (function(rmdfile, ...) { rmarkdown::render(rmdfile, output_dir=here::here("Docs"))})
---

@@

#subbing enfranchisement for public private 
Data$public <- relevel(Data$public, ref = "Yes")

@@

WQ1 <- glm(WQ_combined_any ~  public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(WQ1)

@@

ecoli <- glm(HISTORY_OF_E_COLI_PRESENCE_RISK_LEVEL ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(ecoli)

TT <- glm(TREATMENT_TECHNIUQE_VIOLATIONS_RISK_LEVEL ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(TT)

MCL <- glm(PERCENTAGE_OF_SOURCES_EXCEEDING_AN_MCL_RISK_LEVEL ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(MCL)

@@

Affordability1 <- glm(Affordability_combined_any ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Affordability1)

@@

MHI <- glm(PERCENT_OF_MEDIAN_HOUSEHOLD_INCOME_MHI_RISK_LEVEL_BI ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(MHI)

extreme <- glm(EXTREME_WATER_BILL_RISK_LEVEL_BI ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(extreme)

covid <- glm(didnotapplycovid ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(covid)

@@

Accessibility1 <- glm(Accessibility_combined_any ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Accessibility1)

@@

Single_source <- glm(NUMBER_OF_WATER_SOURCES_RISK_LEVEL_BI ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Single_source)

Sourcecapacity_violations <- glm(SOURCE_CAPACITY_VIOLATION_RISK_LEVEL ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Sourcecapacity_violations)

Service_dis <- glm(Service_disruptions ~ public + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Service_dis)

@@

Compositestable <- capture.output(stargazer(compositemodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Water quality", "Affordability", 
                                                    "Accessibility"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(p.valuesWQ1, p.values2, pvaluesAffordability1, p.values2,
                                       pvaluesAccessibility1, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Ownership - private",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                apply.ci = function(x) { 0 }))

@@

WQtable <- capture.output(stargazer(WQmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("E. coli", "Treatment technique violations", "MCL violations"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesecoli, p.values2, pvaluesTT, p.values2,
                                       pvaluesMCL, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Ownership - private",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

AFtable <- capture.output(stargazer(AFmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Unaffordable bill", "Extreme bill",
                                                    "No arrearage relief"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesMHI, p.values2, pvaluesextreme, p.values2, pvaluescovid, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Ownership - private", 
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

Accesstable <- capture.output(stargazer(Accessmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Single source", "Source capacity violations", "Service disruptions"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesSinglesource, p.values2, pvaluesSourcecapacity_violations, p.values2, pvaluesService_dis, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Ownership - private", 
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

>>>>

---
title: "sensitivity_tests_march2025_tables_specialization"
author: "Kristin Dobbin"
date: "2025-04-14"
output: 
  html_document: default
  pdf_document: default
knit: (function(rmdfile, ...) { rmarkdown::render(rmdfile, output_dir=here::here("Docs"))})
---

@@

Data$specialized <- ifelse(Data$Final_inst_update == "City" | 
                          Data$Final_inst_update == "County Waterworks District" |
                          Data$Final_inst_update == "Maintenance District" |
                          Data$Final_inst_update == "Mobile Home Park", "No", "Yes")

Data <- Data %>% mutate(specialized = case_when(PWSID == "CA2800526" ~ "No", .default = specialized), 
                        specialized = case_when(PWSID == "CA2810013" ~ "No", .default = specialized)) #NAPA RIDs are subsidary districts managed by county (along with Glenn county) everywhere else they are independent special districts

Data$specialized <- as.factor(Data$specialized)
summary(Data$specialized)

Data$specialized <- relevel(Data$specialized, ref = "No")

@@

WQ1 <- glm(WQ_combined_any ~  enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(WQ1)

@@

ecoli <- glm(HISTORY_OF_E_COLI_PRESENCE_RISK_LEVEL ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(ecoli)

TT <- glm(TREATMENT_TECHNIUQE_VIOLATIONS_RISK_LEVEL ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(TT)

MCL <- glm(PERCENTAGE_OF_SOURCES_EXCEEDING_AN_MCL_RISK_LEVEL ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(MCL)

@@

Affordability1 <- glm(Affordability_combined_any ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Affordability1)

@@

MHI <- glm(PERCENT_OF_MEDIAN_HOUSEHOLD_INCOME_MHI_RISK_LEVEL_BI ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(MHI)

extreme <- glm(EXTREME_WATER_BILL_RISK_LEVEL_BI ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(extreme)

covid <- glm(didnotapplycovid ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(covid)

@@

Accessibility1 <- glm(Accessibility_combined_any ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Accessibility1)

@@

Single_source <- glm(NUMBER_OF_WATER_SOURCES_RISK_LEVEL_BI ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Single_source)

Sourcecapacity_violations <- glm(SOURCE_CAPACITY_VIOLATION_RISK_LEVEL ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Sourcecapacity_violations)

Service_dis <- glm(Service_disruptions ~ enfranchisement_final + specialized + POPULATION + Source + Purchased + MHI + Percent.renter + Percent.white, data = Data, family= binomial)
summary(Service_dis)

@@

Compositestable <- capture.output(stargazer(compositemodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Water quality", "Affordability", 
                                                    "Accessibility"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(p.valuesWQ1, p.values2, pvaluesAffordability1, p.values2,
                                       pvaluesAccessibility1, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Limited enfran.", "No enfran.", "Specialized - yes",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                apply.ci = function(x) { 0 }))

@@

WQtable <- capture.output(stargazer(WQmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("E. coli", "Treatment technique violations", "MCL violations"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesecoli, p.values2, pvaluesTT, p.values2,
                                       pvaluesMCL, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Limited enfran.", "No enfran.", "Specialized - yes",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

AFtable <- capture.output(stargazer(AFmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Unaffordable bill", "Extreme bill",
                                                    "No arrearage relief"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesMHI, p.values2, pvaluesextreme, p.values2, pvaluescovid, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Limited enfran.", "No enfran.", "Specialized - yes",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

Accesstable <- capture.output(stargazer(Accessmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Single source", "Source capacity violations", "Service disruptions"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesSinglesource, p.values2, pvaluesSourcecapacity_violations, p.values2, pvaluesService_dis, p.values2),
                                 omit.stat = c("ll"),
                                 covariate.labels = c("Limited enfran.", "No enfran.", "Specialized - yes",
                                                      "Population", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))
